---
title: "Ball Drop Example, No Bias"
author: "Grant Hutchings"
date: "2/23/2022"
output: pdf_document
---

In this example we consider the experiment of dropping balls of varying radii from a tower and recording the time at certain distances during the fall. We will generate time data at distance $d$ from the equation $$
t(d) = \frac{acosh(\exp\{Cd/R\})}{\sqrt{Cg/R}}
$$ where $C$ is the coefficient of drag, $R$ is the radius of the ball, and $g$ is the gravitational constant. The computer simulations will be evaluated over a space filling design of $(R,C)$ pairs in the domain $R\in(.1,2),\;C\in(.01,.5)$.

This tutorial details emulation and prediction using library functions.

```{r , echo=FALSE}
t_at_d = function(C,d,R,g){
  (acosh(exp(C*d/R)))/(sqrt(C*g/R))
}

# number of x inputs
p.x = 2
# number of simulations
m = 98

# sim data
set.seed(11)
# create design over (R,C) on [0,1]
X.sim = lhs::create_oalhs(m,p.x,T,F)
# put inputs on physically relavant scale
X.range = matrix(c(.1,2,.01,.5),nrow=p.x,ncol=2,byrow = T)
X.sim[,1] = X.sim[,1] * (X.range[1,2]-X.range[1,1]) + X.range[1,1]
X.sim[,2] = X.sim[,2] * (X.range[2,2]-X.range[2,1]) + X.range[2,1]
plot.sample = sample(1:m,min(m,1000))
pairs(X.sim[plot.sample,],labels = c('R','C'))

# generate simulations
y.ind.sim = as.matrix(seq(1,25,1)) # distance (meters)
Y.sim = matrix(nrow=length(y.ind.sim),ncol=m)
for(i in 1:m){
  Y.sim[,i] = t_at_d(C=X.sim[i,2],d=y.ind.sim,R=X.sim[i,1],g=9.8)
}
matplot(Y.sim[,plot.sample],type='l',xlab='distance (m)',ylab='time (s)',lty=2)
```

```{r build FlaGP data object}
flagp.data = flagp(X.sim = X.sim, Y.sim = Y.sim, n.pc = 2,
                   ls.m = 5, verbose=T) 
```

```{r, echo=F}
plot(flagp.data,xlab='time (s)',ylab='distance (m)')
```

# Prediction

We generate new synthetic data and compare predictions to data. This problem is incredibly simple, and we have a huge number of data points (10,000) in only 2 input dimensions, so predictions are accurate and emulator uncertainty is very small.

```{r, echo=F}
set.seed(11)
n.pred = 101
X.pred = lhs::create_oalhs(n.pred,p.x,T,F)
X.pred[,1] = X.pred[,1] * (X.range[1,2]-X.range[1,1]) + X.range[1,1]
X.pred[,2] = X.pred[,2] * (X.range[2,2]-X.range[2,1]) + X.range[2,1]
Y.pred = matrix(nrow=length(y.ind.sim),ncol=nrow(X.pred))
for(i in 1:ncol(Y.pred)){
  Y.pred[,i] = (t_at_d(C=X.pred[i,2],d=y.ind.sim,R=X.pred[i,1],g=9.8))
}

flagp.pred = predict(flagp.data,
                     X.pred.orig=X.pred,
                     n.samples = 1000,
                     conf.int = T)
cat('pred time:',flagp.pred$pred.time[3],'s \n')
cat('RMSE:',mean(sqrt((flagp.pred$y.mean - Y.pred)^2)),'\n')
cat('MAPE:',median(100*abs((flagp.pred$y.mean - Y.pred)/Y.pred)),'\n')

plot.id = c(1,5,10)
matplot(Y.pred[,plot.id],type='l',col='black',lty=1,xlab='distance (m)',ylab='time (s)')
matplot(flagp.pred$y.mean[,plot.id],type='l',lty=1,col='darkorange',add=T)
matplot(flagp.pred$y.conf.int[1,,plot.id],type='l',lty=2,col='lightblue',add=T)
matplot(flagp.pred$y.conf.int[2,,plot.id],type='l',lty=2,col='lightblue',add=T)
```
